\documentclass[11pt]{article}
\usepackage[T1]{fontenc}	%special characters
\usepackage[utf8]{inputenc}	%special characters
\usepackage{lmodern,textcomp}% Euro Symbol

\usepackage{hyperref}
\usepackage[margin=1in]{geometry} %article layout margins
\usepackage{tabularx}		%tabulars width fixed textwidth
\usepackage{multicol}	%2 columns in Skills
\usepackage{graphicx}
\usepackage{sectsty}

\begin{document}
\noindent Dear Account Verification Team, \\

\noindent I am Dirk Hornung a former theoretical physics Ph.D. student with 
passion for technology and computer science. Since the age of fourteen, I am
daily programming. With every project, I try to learn new
technologies. I have a huge inner drive in combination with an entrepreneurial
spirit, which has lead to the creation of seven small companies during my time
being. Currently, I want to build a career in one of the top tech companies,
like Google.

\section*{Why Google?}
Google is known to be cutting-edge. It has a tremendous reputation and a huge
influence on my community. This summer I spend time studying distributed
systems and artificial intelligence. I was surprised how Google is driving our
ecosystem with technologies like Tensorflow, Google File System (Hadoop) and
many more. Google should be the best place for me to grow. I would very much
enjoy the company of skilled coworkers and a supportive team to solve
challenges concerning Account Verification.

\section*{Why me?}
I have the following qualifications relevant for a Full-Stack Engineer position:
\begin{itemize}
  \item Experience working as Full-Stack Developer
  \item Solid foundation in computer science, algorithms and data structures
  \item Excellent analytical, troubleshooting and communication skills
  \item Experience programming in HTML, CSS, TypeScript, Python and C++
  \item Quick and motivated learner
\end{itemize}

\noindent I am convinced that my strong background in computer science, together
with my motivation and communication skills would be of great value to Google.\\

\noindent Best regards,\\
Dr. Dirk Hornung \\

 \end{document}